\myTitle

### 2024-11-19 tex/supplemental-text.tex
Cassie's edits on supplement

We used the whole genome sequencing data from \citet{thompson2020complex} to seek variants with
large allele frequency differences between winter-run Chinook salmon and all the other
Chinook salmon ecotypes in the Central Valley of California (CCV).  Because winter-run Chinook are
already highly differentiated from all others, we did not pursue an association study as used
for identifying the late-fall-run associated variants.  Rather, we first identified regions with a high
density of variants with large allele frequency differences between winter-run and non-winter-run
fish in the CCV\@. Subsequently we identified SNPs within those regions with particularly
large allele frequency differences.  This approach was taken to avoid targeting single, isolated SNPs
with large allele frequency differences that may have resulted merely from sampling variation, which was a
concern because we had whole genome sequencing data from only 16 winter run fish.

>>>>

We used the whole genome sequencing data from \citet{thompson2020complex} to seek variants with
large allele frequency differences between winter-run Chinook salmon and all the other
Chinook salmon ecotypes in the Central Valley of California (CCV).  Because winter-run Chinook salmon are
already highly differentiated from all others, we did not pursue an association study as used
for identifying the late-fall-run associated variants.  Rather, we first identified regions with a high
density of variants with large allele frequency differences between winter-run and non-winter-run
fish in the CCV\@. Subsequently we identified SNPs within those regions with particularly
large allele frequency differences.  This approach was taken to avoid targeting single, isolated SNPs
with large allele frequency differences that may have resulted merely from sampling variation, which was a
concern because we had whole genome sequencing data from only 16 winter run fish.
